Exploring Compiler Optimization Techniques

### 2014-11-12 doc/paper.tex
Added dragon citation

Code optimization is most often done by first translating the source code
(as read by a \textit{lexer} and interpreted by a \textit{parser}) into an
\textit{intermediate form}, which is subsequently converted into assembly. Such
an intermediate form must be designed in such a way that it can be analyzed and
optimized easily.

@@

May be converted (by the \textit{front-end}) into the following intermediate form
(this intermediate form is described in \ref{sec:irused}):

@@

\begin{thebibliography}{9}
  \bibitem{llvm_ir}
  \emph{LLVM Language Reference Manual}. (2014) Consulted on 2014/11/11,
  \url{http://llvm.org/docs/LangRef.html}

>>>>

Code optimization is most often done by first translating the source code
(as read by a \textit{lexer} and interpreted by a \textit{parser}) into an
\textit{intermediate form}, which is subsequently converted into assembly. Such
an intermediate form must be designed in such a way that it can be analyzed and
optimized easily.\cite{dragon}

@@

May be converted (by the \textit{front-end}) into the following intermediate form
(this intermediate form is described in section~\ref{sec:irused}):

@@

\begin{thebibliography}{9}
  \bibitem{dragon} Aho et al.
  \emph{Compilers: Principles, Techniques And Tools}.
  (1988)

  \bibitem{llvm_ir}
  \emph{LLVM Language Reference Manual}. (2014) Consulted on 2014/11/11,
  \url{http://llvm.org/docs/LangRef.html}
